A Switching Planner for Combined Task and Observation Planning

### 2010-11-27 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/conc.tex
new conclusion, and typos in prop. section

An obvious theoretical criticism of switching continual planning
concerns interleaved sequential and contingent sessions failing to
make any progress towards the objectives. For example, in the worst
case we can have each sequential session producing an identical plan,
and each decision-theoretic session rejecting it without further
sensing. Although this has not been an issue in our work so far, it
must be dealt with rigorously moving forward. We suggest that a good
way of mitigate this problem is by using a {\em motivational}
component that maintains a {\em dynamic} reward model for sensing.

>>>>

The most pressing item for future research, is to develop a scheme
whereby the serial planner can relax {\em executability} assumptions,
so that conformant (or semi-conformant) plans can be executed without
interruption by a contingent session. A more general criticism of
switching continual planning concerns interleaved sequential and
contingent sessions failing to make any progress towards the
objectives. For example, in the worst case we can have each sequential
session producing an identical plan, and each decision-theoretic
session rejecting it without further sensing. Although this has not
been an issue in our work so far, it must be dealt with rigorously
moving forward. We suggest that a good way of mitigate this problem is
by developing a {\em motivational} component that maintains a {\em
dynamic} reward model whose limiting behaviour prevents that switching
deadlock.

### 2010-11-27 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/prop-dtp.tex
new conclusion, and typos in prop. section

Until now we have discussed the POMDP in terms of propositions and
percepts. In order to address belief revision and utility it is
convenient to consider the underlying decision process in a flat
format. This is given by the tuple
$\langle \states, \bstate_0, \actions, \transProb, \reward,
\observations, \obsDist \rangle$. Here $\bstate_0$ is the initial
belief-state, \states\ is the finite set of reachable propositional
states, \actions\ is the finite set of actions, and \observations\ is
the finite set of reachable observations (i.e., perceptual states).
Where $\state, \state' \in \states$, $a \in \actions$, from $\mu$ we
have a state transition function $\transProb(\state, \action,
\state')$ giving the probability of a transition from state $s$ to
$s'$ if $a$ is applied. For any $\state$ and $\action$ we have
$\sum_{\state' \in \states} \transProb(\state, \action, \state') = 1$.
%%
Function $\reward:\states \times \actions \to \Re$ is a bounded real
valued reward function. Therefore a finite positive constant $c$
exists so that for all $\state \in \states$ and $\action \in
\actions$, $|\reward(\state, \action)| < c$. We model costs as
negative rewards.
%%
From $\psi$ we have that for each $\state \in \states$ and action
$\action \in \actions$, an observation $\observ \in \observations$ is
generated independently according to a probability distribution
$\obsDist(\state, \action)$. We denote $\obsDist_\observ(\state,
\action)$ the probability of getting observation $\observ$ in state
$\state$. For $\state$ and $\action$ we have $\sum_{\observ \in
\observations} \obsDist_\observ(\state, \action) = 1$.

>>>>

Until now we have discussed the POMDP in terms of propositions and
percepts. In order to address belief revision and utility it is
convenient to consider the underlying decision process in a flat
format. This is given by the tuple
$\langle \states, \bstate_0, \actions, \transProb, \reward,
\observations, \obsDist \rangle$. Here, $\bstate_0$ is the initial
belief-state, \states\ is the finite set of reachable propositional
states, \actions\ is the finite set of actions, and \observations\ is
the finite set of reachable observations (i.e., perceptual states).
Where $\state, \state' \in \states$, $a \in \actions$, from $\mu$ we
have a state transition function $\transProb(\state, \action,
\state')$ giving the probability of a transition from state $s$ to
$s'$ if $a$ is applied. For any $\state$ and $\action$ we have
$\sum_{\state' \in \states} \transProb(\state, \action, \state') = 1$.
%%
Function $\reward:\states \times \actions \to \Re$ is a bounded real
valued reward function. Therefore a finite positive constant $c$
exists so that for all $\state \in \states$ and $\action \in
\actions$, $|\reward(\state, \action)| < c$. We model costs as
negative rewards.
%%
From $\psi$ we have that for each $\state \in \states$ and action
$\action \in \actions$, an observation $\observ \in \observations$ is
generated independently according to a probability distribution
$\obsDist(\state, \action)$. We denote $\obsDist_\observ(\state,
\action)$ the probability of getting observation $\observ$ in state
$\state$. For $\state$ and $\action$ we have $\sum_{\observ \in
\observations} \obsDist_\observ(\state, \action) = 1$.
